### 2019-03-21 0_abstract.tex

\begin{abstract}
% 153 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelops of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench consists of a configurable \emph{task graph} with one task per
point in an iteration space, and dependencies between tasks determined
by a dependence relation. Tasks can execute a variety of kernels,
including compute- and memory-bound, and task dependencies carry
payloads of configurable size, enabling communication-bound use
cases. Multiple task graphs can be executed to enable task
parallelism.

We conduct a comprehensive comparative study with implementations of
Task Bench in 13 programming systems on up to 256 Haswell nodes of the
Cori supercomputer. We use a novel metric, \emph{minimum effective
  task granularity} to study the baseline runtime overhead of each
system and the impact of varying dependence patterns and number of
dependencies. We also study each system's scalability, and ability to
hide communication and mitigate load imbalance.
\end{abstract}

>>>>

\begin{abstract}
% 149 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelops of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench consists of a configurable \emph{task graph} with one task per
point in an iteration space, and dependencies between tasks determined
by a \emph{dependence relation}. Tasks execute a variety of kernels,
including compute- and memory-bound, and dependencies carry payloads
of configurable size, enabling communication-bound scenarios. Multiple
task graphs can be executed to enable task parallelism.

We conduct a comprehensive study with implementations of Task Bench in
13 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We use a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each system
and the impact of varying dependence patterns and numbers of
dependencies. We also study each system's scalability, and ability to
hide communication and mitigate load imbalance.
\end{abstract}
